% code_and_data.tex
\label{sec:code_and_data}

\subsection{Repository layout}

The catalogue's source tree is laid out as follows:

\begin{itemize}
\item \texttt{src/utilities/automorphism\_centralizer\_extended.py}
  -- Paper~II Phase~3 centralizer enumeration, reproduced verbatim.
  Builds the 143-element Pauli\,$\otimes$\,Pauli\,$\otimes$\,Gell-Mann
  tensor basis of $\mathfrak{su}(12)$, filters to the 71-dim
  centralizer of the bipartite tick rule, classifies into 7
  tensor-signature categories.
\item \texttt{src/utilities/aut\_centralizer\_extras\_commutators.py}
  -- Paper~II Phase~3 bracket-classification script, reproduced
  verbatim.  Computes all 708 $[\text{extras}, \text{SM}]$ brackets
  and 1711 $[\text{extras}, \text{extras}]$ brackets, classifies
  each as zero / in\_SM / in\_extras / mixed.
\item \texttt{src/utilities/generator\_zoo.py} (planned for
  v1.0) -- the catalogue script proper.  Extends the two
  inherited scripts above with stable per-generator names, an
  $(SU(3), SU(2))$ irrep tag, a 3-bit tensor-factor action tag,
  and a bracket-class lookup; emits a JSON catalogue and a
  \LaTeX{} longtable fragment.
\item \texttt{data/generator\_catalogue.json} (planned for v1.0)
  -- machine-readable emit of the catalogue, one record per
  generator.
\item \texttt{notes/} -- four Paper~II notes reproduced with
  Provenance prefixes, providing the textual companion to the
  inherited scripts.
\item \texttt{paper/sections/generator\_zoo.tex} (planned for v1.0)
  -- the catalogue appendix proper (longtable + reader's map).
\end{itemize}

\subsection{Reproducing the v0.1 audit table}

Every \texttt{PASS} row in Table~\ref{tab:audit} is reproduced by:

\begin{verbatim}
python -u src/utilities/automorphism_centralizer_extended.py
python -u src/utilities/aut_centralizer_extras_commutators.py
\end{verbatim}

The two scripts run independently; each prints a structured report
of the centralizer dimension, the SM-aligned vs extras split, and
the bracket-classification counts.  Total runtime is on the order
of minutes on a modern laptop (the second script computes 2419
symbolic $12 \times 12$ commutators and classifies each by rank).
