% introduction.tex

\label{sec:introduction}

This document is the companion catalogue to Paper~II of the A=1
Discrete Causal Lattice series~\cite{menendez2026sm}, which
established Eq.~(137) of Paper~I~\cite{menendez2026geometry} as a
structural-equality conjecture between the per-site automorphism
algebra of the bipartite octahedral lattice and the Lie algebra
$\mathfrak{so}(3,1) \oplus \mathfrak{su}(3) \oplus \mathfrak{su}(2)
\oplus \mathfrak{u}(1)$.  Paper~II's Phase~3 enumeration produced
the sharper result that the discrete-Hermitian centralizer of the
bipartite tick rule on the per-site $\mathbb{C}^{12}$ amplitude has
dimension~71, with structural decomposition $\mathfrak{su}(6)_+
\oplus \mathfrak{su}(6)_- \oplus \mathfrak{u}(1)$.  The
12-dimensional Standard Model gauge subalgebra is contained in
this centralizer; the remaining 59 generators are the
``extras''~\cite{georgi1999lie}, structurally $(\mathbf{8},
\mathbf{3})$ leptoquark-flavoured plus chirality-$\sigma_x$-twisted
SM-flavoured.

That count -- 12 SM, 59 extras, 71 total -- is the input to this
catalogue.  Paper~II's prose treats the 59 extras at the level of
their representation-theoretic content and their bracket structure;
it does not give them individual names, irrep tags per generator,
or a machine-readable form that downstream papers can consume
without re-running the enumeration.  This zoo fills that gap.

\subsection{Scope}
\label{subsec:scope}

What this document is:

\begin{itemize}
\item A \emph{catalogue}, not a paper of new results.  All
      algebraic content is inherited from Paper~II Phase~3.
\item A persistent \emph{naming convention} for each of the 71
      centralizer generators.  Names are stable across catalogue
      revisions so that follow-on papers can cite generators by
      name.
\item A \emph{taxonomy} along several orthogonal axes (source
      $\mathfrak{su}(6)$ factor; $(SU(3), SU(2))$ irrep content;
      tensor-factor action; bracket class against every other
      generator).
\item A \emph{machine-readable emit} (JSON) plus a printable
      longtable rendering, so external work can consume the
      catalogue either programmatically or by reading.
\end{itemize}

What this document is not:

\begin{itemize}
\item A re-derivation of Paper~II Phase~3.  The dimensional and
      structural results are cited, not re-proved here.
\item A statement of physical interpretation.  The
      decoherence-channel hypothesis of Paper~II's
      \texttt{notes/extras\_as\_a1\_accounting.md} (DRAFT) is
      reproduced as an appendix note, marked clearly as
      conjectural; the catalogue itself records only the algebraic
      facts.
\item A successor to Paper~II.  This is companion infrastructure,
      not a Paper~III.
\end{itemize}

Table~\ref{tab:audit} records the catalogue's audit-row status.
Most rows inherit \texttt{PASS} from Paper~II Phase~3; the rows
specific to the zoo's value-add (stable naming, irrep tagging,
JSON emit, LaTeX renderer) are \texttt{STUB} in the v0.1 draft and
will flip to \texttt{PART}/\texttt{PASS} as Phase~2 of this
catalogue is executed.

%% Audit table embedded here so the reader meets it before any
%% claim that depends on a status entry.
\input{sections/audit_table}
