% reproducibility.tex
\label{sec:reproducibility}

\begin{itemize}
\item \textbf{Environment.}  Python~3 with \texttt{sympy},
      \texttt{numpy}, \texttt{matplotlib}, \texttt{pytest}.
      Exact dependency list in \texttt{virtual-env-requirements.txt}.
      The \texttt{setup.sh} / \texttt{setup.cmd} scripts create a
      \texttt{.venv} and install everything.

\item \textbf{Build the paper.}  From a fresh clone, with the venv
      activated:
      \begin{verbatim}
./build.sh paper        # POSIX / MSYS2 UCRT64 on Windows
build.cmd paper         # Windows cmd / PowerShell
      \end{verbatim}
      runs \texttt{pdflatex} three times and \texttt{bibtex} once,
      producing \texttt{paper/main.pdf}.

\item \textbf{Verify the headline result.}  The two inherited
      Paper~II scripts together reproduce every \texttt{PASS} row
      in Table~\ref{tab:audit}:
      \begin{verbatim}
python -u src/utilities/automorphism_centralizer_extended.py
python -u src/utilities/aut_centralizer_extras_commutators.py
      \end{verbatim}
      Each prints a structured report ending in either ``\texttt{PASS}''
      or a count-mismatch error.  Total runtime: a few minutes.

\item \textbf{Run the master audit roll-up.}  From the repo root:
      \begin{verbatim}
python audit_universe.py
      \end{verbatim}
      parses \texttt{paper/sections/audit\_table.tex} and reports
      the declared status of every row.  Rows whose evidence is
      analytical (script output cited as
      \texttt{src/utilities/*.py}) are reported as-is.

\item \textbf{Where to look next.}  The four notes under
      \texttt{notes/} (each prefixed with a Provenance block)
      provide the textual companion to the algebraic results.
      Start with \texttt{notes/aut\_centralizer\_enumeration.md}
      for the structural identification of the 71-dim centralizer
      as $\mathfrak{su}(6)_+ \oplus \mathfrak{su}(6)_- \oplus
      \mathfrak{u}(1)$; then
      \texttt{notes/aut\_centralizer\_extras\_commutators.md}
      for the bracket-classification reading; then (DRAFT)
      \texttt{notes/extras\_as\_a1\_accounting.md} for the
      conjectural decoherence-as-projection physical
      interpretation.
\end{itemize}
