\documentclass[12pt, letterpaper]{article}

%% Build from the paper/ directory:
%%   cd paper && pdflatex main.tex
%% or use the root build system:
%%   make paper          (from repo root)
%%   ./build.sh paper    (POSIX)
%%   build.cmd paper     (Windows cmd)

\input{macros/packages}
\input{macros/commands}

%% Page geometry (also set here as a fallback in case the package path fails)
\geometry{top=1in, bottom=1in, left=1in, right=1in}

%% ---------------------------------------------------------------
%% TITLE PAGE
%% ---------------------------------------------------------------

\title{The dcl-generator-zoo:\\
       A Catalogue of the 71-Dimensional Per-Site\\
       Automorphism Algebra of the A=1 Discrete Causal Lattice%
       \thanks{Version 0.1-DRAFT.  Companion artifact to the A=1
       Discrete Causal Lattice series; built on the Phase~3
       centralizer enumeration of
       \emph{Geometry Forces Physics} (Paper~II,
       \href{https://doi.org/10.5281/zenodo.20240736}{DOI:
       10.5281/zenodo.20240736}), which itself builds on
       \emph{Geometry First} (Paper~I,
       \href{https://doi.org/10.5281/zenodo.20078529}{DOI:
       10.5281/zenodo.20078529}).  This catalogue is intended as
       the canonical reference for downstream papers in the series
       and for external work building on the framework's per-site
       algebraic structure.  DOI for this catalogue to be assigned
       at v1.0 deposit.}}
\author{Jack Menendez\\
        \small Eugene, OR\\
        \small ORCID: \href{https://orcid.org/0009-0003-1166-307X}{0009-0003-1166-307X}\\
        \small \href{mailto:jackdmenendez@gmail.com}{jackdmenendez@gmail.com}}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
    \input{sections/abstract}
\end{abstract}

%% ---------------------------------------------------------------
%% FRONT-MATTER NOTICES (after abstract per author preference)
%% ---------------------------------------------------------------

\medskip
\noindent\textbf{Keywords.}  A=1 Discrete Causal Lattice; per-site
automorphism algebra; centralizer; $\mathfrak{su}(6)$; Standard
Model gauge group; leptoquark; chirality; bracket structure; broken
symmetry; sympy verification.

\medskip
\noindent\textbf{License.}  Paper text and figures: Creative Commons
Attribution 4.0 (CC BY 4.0).  Source code in the companion
repository: MIT License.

\medskip
\noindent\textbf{Data availability.}  The catalogue, its
verification scripts, and the \LaTeX{} source for this document are
publicly available at the GitHub repository
\nolinkurl{github.com/JackDMenendez/dcl-generator-zoo}.  The
load-bearing centralizer enumeration scripts
\nolinkurl{automorphism_centralizer_extended.py} and
\nolinkurl{aut_centralizer_extras_commutators.py} were introduced
in Paper~II~\cite{menendez2026sm} and are reproduced here verbatim
as inherited evidence; the zoo's own enumeration script
\nolinkurl{generator_zoo.py} (planned for v1.0) extends them with
stable naming, irrep tagging, and JSON / \LaTeX{} rendering.

%% ---------------------------------------------------------------
%% RELEASE NOTES (only at release time)
%% ---------------------------------------------------------------
%% \bigskip
%% \noindent\textbf{Release notes for vX.Y (since vX.Y-1).}
%% \begin{itemize}
%% \item Item 1.
%% \end{itemize}

%% \emph{Status legend used throughout.}  \texttt{PASS} / \texttt{PART}
%% / \texttt{STUB} / \texttt{FAIL} -- see Table~\ref{tab:audit}.

\newpage
\tableofcontents
\newpage

%% ============================================================
%% MAIN
%% ============================================================
\section{Introduction}
\input{sections/introduction}

%% Future sections (Phase~2 of this catalogue):
%%   \section{Naming convention}
%%   \section{Tensor-factor action tags}
%%   \section{Representation-theoretic content}
%%   \section{Bracket-class lookup}
%%   \section{JSON emit and downstream consumption}
%%   \section{Generator zoo} (the catalogue appendix proper)

\section{Conclusion}
\input{sections/conclusion}

\section*{Acknowledgements}
\input{sections/acknowledgements}

%% ============================================================
%% APPENDICES
%% ============================================================
\appendix

\section{Generator Zoo}
\input{sections/generator_zoo}

\section{Code and Data}
\input{sections/code_and_data}

\section{Reproducibility Quickstart}
\input{sections/reproducibility}

%% ============================================================
\bibliographystyle{unsrt}
\bibliography{paper-bib/references}

\end{document}
